---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.dev = "grDevices::png",
  dpi = 300L,
  dev.args = list(),
  fig.ext = "png",
  fig.height=8,
  fig.width=12,
  fig.retina = 2L,
  fig.align = "center"
)
```

# scstruc

The package for analysing the gene regulatory network based on the Bayesian network structure of single-cell transcriptomics data. The function works with `SingleCellExperiment`.

<!-- badges: start -->
[![R-CMD-check](https://github.com/noriakis/scstruc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/noriakis/scstruc/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->


## Installation

Using `devtools`:

```{r, eval=FALSE}
devtools::install_github("noriakis/scstruc")
```

For using the CCDr algorithm in the latest R version, please install `ccdrAlgorithm` package from the following repository, which removes the `||` usage error.

```{r, eval=FALSE}
devtools::install_github("noriakis/ccdrAlgorithm")
```

## Examples

```{r message=FALSE, warning=FALSE, fig.width=12, fig.height=12}
library(scran)
library(scstruc)
library(ggraph)
library(bnlearn)
sce <- mockSCE()
sce <- logNormCounts(sce)
included_genes <- sample(row.names(sce), 100)
gs <- scstruc(sce, included_genes, changeSymbol=FALSE)
plotNet(gs$net, gs$data, showText=FALSE)
```

Using the bootstrapping, the averaged network is obtained.

```{r message=FALSE, warning=FALSE, fig.width=8, fig.height=8}
library(glmnet)
gs2 <- scstruc(sce, included_genes, algorithm="glmnet_BIC", boot=TRUE,
               changeSymbol=FALSE, R=20)
plotAVN(gs2$net, sizeRange=c(1,3))
```
